Agile Monitoring of Evolving Web Services

### 2018-03-28 restructured.tex
.

  \newpage
TODO: TALK ABOUT THE DATABASE...

@@

@@

\begin{figure}[h!]
  \centering
  \subfloat[overview of the tracked endpoints]{\includegraphics[width=0.8\columnwidth]{overview}\label{fig:overview}}
  \caption{Some of the available views\label{fig:views}}
\end{figure}

@@

  \begin{figure*}[h!]
    \centering
    \includegraphics[width=\linewidth]{outliers}
    \caption{Automatically collected outlier information}
    \label{fig:figure1}
  \end{figure*}
  \newpage
  \section{Automated outlier detection and monitoring}

@@

>>>>

@@

\begin{figure*}[h!]
  \centering
  \subfloat[overview of the tracked endpoints]{\includegraphics[width=1.5\columnwidth]{overview}\label{fig:overview}}
  \caption{Some of the available views\label{fig:views}}
\end{figure*}

@@

  \begin{figure*}[h!]
    \centering
    \includegraphics[width=\linewidth]{outliers}
    \caption{Automatically collected outlier information}
    \label{fig:figure1}
  \end{figure*}
  \newpage
  \subsection{Performance Insight: Automated outlier detection and monitoring}

\begin{figure*}[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{utilization-evolution}
  \caption{The Performance Evolution of the \epTranslations endpoint}
  \label{fig:tee}
\end{figure*}

@@

@@

  \newpage
TODO: TALK ABOUT THE METAMODEL...

    \begin{figure}[ht!]
      \centering
        \includegraphics[width=0.8\linewidth]{db_schema}
        \caption{The model that supports the views presented in this paper}
        \label{fig:sep}
    \end{figure}
